Add Amicus Measures

### 2022-04-11 data-cleaning/05-add-amicus-measures.Rmd
mv + rnm

# data/processed amicus files/amicus_text_clean_512.csv
amicus <- box_read("939714323391")

@@

```{r}
final %>% head()
```

@@

```{r}
box_write(final,
           file_name = "amicus_text_clean_512_vars.csv",
           dir_id = 145990409196)
```

>>>>

# data/processed amicus files/amicus_clean_512_no_stride.csv
amicus <- box_read("942789542605")

@@

```{r}
final %>% head()
```
Ensure no NAs

```{r}
final %>% select_if(function(x) any(is.na(x))) %>% 
  summarise_each(funs(sum(is.na(.))))
```

Missing this brief. I don't see it in Holly's data?

```{r}
amicus %>% filter(id == 861822406799) %>% distinct(brief) %>% pull(brief)
```

@@

```{r}
box_write(final,
           file_name = "amicus_clean_512_no_stride_vars.csv",
           dir_id = 145990409196)
```
